Reanalysis Step 2: Multiple Imputation

### 2025-08-26 reanalysis-2-multiple_imputation.qmd
test

# Show predictor matrix summary
# Calculate average predictors (excluding self-predictions)
avg_predictors <- round(mean(rowSums(pred_matrix)), 1)
predictors <- names(which(colSums(pred_matrix) > 0))

@@

Each variable uses an average of **`r avg_predictors`** predictors.

**ID variables properly excluded from predictors:** `r if(ids_excluded) "✓ Yes" else "✗ No"`

>>>>

# Show predictor matrix summary
# Get the number of predictors for each variable
predictors_per_var <- rowSums(pred_matrix)

# Separate by variable type
id_vars_pred <- predictors_per_var[c("row_id", "e_mrn_deidentified")]
imputed_vars_pred <- predictors_per_var[vars_to_impute]
other_vars_pred <- predictors_per_var[!names(predictors_per_var) %in% c("row_id", "e_mrn_deidentified", vars_to_impute)]

# Calculate meaningful statistics
n_predictors_for_imputed <- if(length(imputed_vars_pred) > 0) unique(imputed_vars_pred)[1] else NA
predictors <- names(which(colSums(pred_matrix) > 0))

@@

**Number of predictors used:**
- For variables being imputed: **`r if(!is.na(n_predictors_for_imputed)) n_predictors_for_imputed else 0`** predictors each
- For ID variables: **0** predictors (excluded from imputation)

**ID variables properly excluded from predictors:** `r if(ids_excluded) "Yes" else "No"`
